Tom Stafford

### 2025-08-01 index.qmd
update

![](tom_2020.jpg){width="25%"}

@@

I direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science. I teach a module on [Data Management and Visualisation](https://tomstafford.github.io/psy6422/).

At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research. As Research Practice Lead, I represent the University of Sheffield on the [UK Reproducibility Network](https://www.ukrn.org/), for which I chair the national [UKRN Institutional Leads group](https://www.ukrn.org/institutional-leads/).

@@

@@

>>>>

![](images/tom_2020.jpg){width="50%"}

@@

::: {.callout-tip title="News!"}
From 1st September 2025 - 31st August 2026 I am on leave from the University of Sheffield. During this time I will be on secondment to the [Research on Research Institute](https://researchonresearch.org/), as well as pursing writing projects. Subscribe for updates on [tomstafford.substack.com/](https://tomstafford.substack.com/).
:::

@@

Previously, I was Director for the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science. You can read more about the flagshiop module I designed and taught here: [PSY6422 Data Analysis and Visualisation](https://tomstafford.github.io/psy6422/).

From 2020 to 2025 I held the Research Practice Lead for the University of Sheffield, an institution-wide role with a remit to encourage practices which support robust and trusted research. As Research Practice Lead, I represented the University of Sheffield in the [UK Reproducibility Network](https://www.ukrn.org/), for which I chaired the national [UKRN Institutional Leads group](https://www.ukrn.org/institutional-leads/) 2023 - 2025.

@@

## More

* [Research](research.html)
* [Papers](papers.html)
* [Writing](writing.html)
* [Talks](talks.html)
* [Teaching](teaching.html)
* [Supervision](supervision.html)
* [Done](done.html)
* [News](news.html)
